\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Assessing economic inequality with tax data - Switzerland from 1945 to 2010}

### 2014-06-29 paper/options/global_r_options.Rnw
compile-o-mat

  # messages 
  opts_chunk$set(warning=FALSE)
  # code evaluation 
  opts_chunk$set(eval=TRUE)
  # code decoration
  opts_chunk$set(tidy=TRUE, prompt=TRUE, comment='##', highlight=TRUE, size='normalsize')
  # cache options
  opts_chunk$set(cache.path='cache/')  
  # Caching on by default
  opts_chunk$set(cache=FALSE)
  # plot options 
  #if("tikzDevice" %in% rownames(installed.packages()) == TRUE) {
	# opts_chunk$set(fig.path='usr/graphics/dynamic/', dev='tikz', fig.keep='high', fig.show='hold')  
  #} else {
	# opts_chunk$set(fig.path='usr/graphics/dynamic/', dev='pdf', fig.keep='high', fig.show='hold')  
  #}

>>>>

  # messages 
  opts_chunk$set(warning=FALSE)
  # code evaluation 
  opts_chunk$set(eval=TRUE)
  # code decoration
  opts_chunk$set(tidy=TRUE, prompt=TRUE, comment='##', highlight=TRUE, size='normalsize')
  # cache options
  opts_chunk$set(cache.path='cache/')  
  # Caching on by default
  opts_chunk$set(cache=TRUE)
  # plot options 
  #if("tikzDevice" %in% rownames(installed.packages()) == TRUE) {
	# opts_chunk$set(fig.path='usr/graphics/dynamic/', dev='tikz', fig.keep='high', fig.show='hold')  
  #} else {
	# opts_chunk$set(fig.path='usr/graphics/dynamic/', dev='pdf', fig.keep='high', fig.show='hold')  
  #}
